Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2022-04-15 doc/manuscript/ESSDmanuscript.Rmd
finish first draft of section 2

## Land use categories
IPCC defines land-use categories to include six categories -- Forest Land, Grassland, Wetlands, Cropland, Settlements, and Other Land [@ipcc_2006_2006].
Sub-divisions include land that has remained in a particular category for >20 years (e.g., Forest Land remaining Forest Land) and land that has been converted from one category to another in the past 20 years (e.g., Cropland converted to Forest Land). 
Forest Land
Definitions of forest are allowed to vary by country, but must be applied consistently.

Inventories are conducted only for managed land, which is defined by IPCC to include "all forests subject to some kind of human interactions (notably commercial management, harvest of industrial round-wood (logs) and fuelwood, production and use of wood commodities, and forest managed for amenity value or environmental protection if specified by the country), with defined geographical boundaries" [@ipcc_good_2003.

>>>>

## Land use categories
IPCC defines land-use categories to include six categories -- Forest Land, Grassland, Wetlands, Cropland, Settlements, and Other Land [@ipcc_2006_2006].
Sub-divisions include land that has remained in a particular category for >20 years (e.g., Forest Land remaining Forest Land) and land that has been converted from one category to another in the past 20 years (e.g., Cropland converted to Forest Land). 
Forest Land is defined as at least 10-30% crown cover of trees with potential to reach a minimum height of 2-5 m *in situ* [@ipcc_good_2003].
Definitions of forest are allowed to vary by country, but must be applied consistently.
Forest Land includes land where vegetation temporarily falls below the threshold values for forest (e.g., due to disturbance), but is expected to exceed those thresholds in the future [@ipcc_good_2003].

Inventories are conducted only for managed land, which is defined by IPCC to include "all forests subject to some kind of human interactions (notably commercial management, harvest of industrial round-wood (logs) and fuelwood, production and use of wood commodities, and forest managed for amenity value or environmental protection if specified by the country), with defined geographical boundaries" [@ipcc_good_2003].
As such, managed land constitutes all or the majority of Forest Land in most countries; however, many countries have not yet reported their approach for defining managed land [@ogle_delineating_2018; @deng_comparing_2021].

### 2022-04-15 doc/manuscript/ESSDmanuscript.tex
finish first draft of section 2

IPCC defines land-use categories to include six categories -- Forest
Land, Grassland, Wetlands, Cropland, Settlements, and Other Land
\citep{ipcc_2006_2006}. Sub-divisions include land that has remained in
a particular category for \textgreater20 years (e.g., Forest Land
remaining Forest Land) and land that has been converted from one
category to another in the past 20 years (e.g., Cropland converted to
Forest Land). Forest Land Definitions of forest are allowed to vary by
country, but must be applied consistently.

Inventories are conducted only for managed land, which is defined by
IPCC to include ``all forests subject to some kind of human interactions
(notably commercial management, harvest of industrial round-wood (logs)
and fuelwood, production and use of wood commodities, and forest managed
for amenity value or environmental protection if specified by the
country), with defined geographical boundaries''
{[}\citet{ipcc_good_2003}.

>>>>

IPCC defines land-use categories to include six categories -- Forest
Land, Grassland, Wetlands, Cropland, Settlements, and Other Land
\citep{ipcc_2006_2006}. Sub-divisions include land that has remained in
a particular category for \textgreater20 years (e.g., Forest Land
remaining Forest Land) and land that has been converted from one
category to another in the past 20 years (e.g., Cropland converted to
Forest Land). Forest Land is defined as at least 10-30\% crown cover of
trees with potential to reach a minimum height of 2-5 m \emph{in situ}
\citep{ipcc_good_2003}. Definitions of forest are allowed to vary by
country, but must be applied consistently. Forest Land includes land
where vegetation temporarily falls below the threshold values for forest
(e.g., due to disturbance), but is expected to exceed those thresholds
in the future \citep{ipcc_good_2003}.

Inventories are conducted only for managed land, which is defined by
IPCC to include ``all forests subject to some kind of human interactions
(notably commercial management, harvest of industrial round-wood (logs)
and fuelwood, production and use of wood commodities, and forest managed
for amenity value or environmental protection if specified by the
country), with defined geographical boundaries'' \citep{ipcc_good_2003}.
As such, managed land constitutes all or the majority of Forest Land in
most countries; however, many countries have not yet reported their
approach for defining managed land
\citep{ogle_delineating_2018, deng_comparing_2021}.
